\documentclass[hidelinks, 12pt, oneside]{article}
\usepackage{bookmark}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{titlesec}
\setcounter{secnumdepth}{4}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{color}


\begin{document}

	\input{./titlepage.tex}
	\tableofcontents
	\newpage
	
	\section{Overview}
	\emph{iCrawler} is a monitoring app available for Android only. The app
	 uses your device's internet connection to send data logs collected from your phone to a desktop-dashboard
	 for review. The app is absolutely free to download.\newline\newline
	 
	 \uppercase{Why use iCrawler:}\newline
	 \begin{itemize}
		\item Child monitoring\newline
		\emph{iCrawler} can be use by parents/guardians to monitor activities that their minor
		 children get up to.	
		\item Employee monitoring\newline
		Companies that give their employees mobile devices can use the \emph{iCrawler} to monitor any 
		unauthorized activities that employees may get up to.
	\end{itemize}
	\newpage
	
	
	\section{Configuration}\newpage
	
	\section{Installation}\newpage
	
	\section{Getting Started}
	Before you download and install \emph{iCrawler}, make sure \emph{iCrawler} supports
	 your phone type. Please check this \href{https://}{\color{blue}here}.\newline\newline
	 To download \emph{iCrawler}, visit this \href{https://}{\color{blue}link} on your phone. Once
	 installed, locate the app icon and run the app.\
	 \begin{itemize}
	 	\item Terms and Conditions\newline
	 	Read the 'Terms and Conditions' on startup and only after accepting them can you proceed, if you
	 	 don't accept you can not use the app.
	 	\item Register new user\newline
	 	First time users need to register after accepting the 'Terms and Conditions'. The user needs to provide
	 	 a working email address and create a new password they will use to login with in future.
	 	\item Login as existing user\newline
	 	Existing users need not to register, simply click 'Existing user' and then login in order to subscribe the 
	 	new device.
	 \end{itemize}
	 \newpage
	 
	 
	\section{Using the App}
	The app runs in the background through out its installation; the user never 
	gets to directly interact with the app there after.
	\newline\newline
	
	\section{Troubleshooting}\newpage
			
\end{document}
